\documentclass{letter}
\signature{Rick Bradley}
\address{5001 Indiana Avenue \ Nashville, TN  37209 \ email: rick@rickbradley.com}
\begin{document}
\begin{letter}{Senator Lamar Alexander \ 455 Dirksen Senate Office Building \ Washington, DC 20510}
\opening{To whom it may concern:}
Senator Alexander,

It is time to weigh in in favor of bringing in John Bolton to testify as a witness in President Trump's impeachment trial.

The Republican party is no longer benefitted by its association with President Trump -- I believe we all hoped it would be, and yet have been left disappointed. As allegations continue to emerge -- and will seemingly continue, and likely grow worse -- about our President's abuses of the power vested in him by our Constitution and our votes, time only reflects worse on our inability to reign him in.

We gave the honest benefit of the doubt, but were left out of his counsels. We can double-down on the President's follies and pay a deep price, or we can face facts and cut our losses.

This moment is the time when Bolton's testimony can put an end to the tenure of this bull-in-the-china shop President. We can move forward with President Pence, regroup and reposition ourselves. It's a painful change of course, but it has upsides rather than only downsides.

You are the retiring august Senator from the Great State of Tennessee. You have little to lose from this President by way of retaliation. Your voice is one that can be heard. You speaking out does great good for the Party, the State, and the United States.

Sincerely,

Rick Bradley

\closing{Sincerely,}
\end{letter}
\end{document}
\end
